---
title: "SIMOA"
author: "Pierre-Olivier Couture"
format: html
editor: visual
---

## Introduction

This is all the code I am going to use for my MSc thesis. I will have it broken
down by the type of analysis I am running and rill include a description of 
everything I am doing. The large titles will represent what I am doing broadly
and the labels in each 'chunk' of code will be more descriptive about what 
exactly I am doing in that chunk. Also, I will include a comment inside each 
chunk which will provide an even more detailed breakdown of what all the codes
are doing. I may even include explanations mid-code to ensure everything is
reproducible and will make it easier when this needs to be replicated later by
myself for publication, or reviewers/MSc committee for confirmation of results.

## Packages

```{r}
#| label: Installing Packages
# Here I will include all the code I need to install the packages I need to 
# conduct my analysis. I will keep adding to this throughout my coding.

install.packages("data.table")
install.packages("tidyverse")

```

```{r}
#| label: Calling in the packages
# Here I will include all the code to call in the packages I have installed. 
# Again, I will update this everytime I need to call-in a new package throughout
# my coding.


```



























































































































































































































































































The `echo: false` option disables the printing of code (only output is displayed).
