---
title: "SIMOA EDITING"
author: "Pierre-Olivier Couture"
format: html
editor: visual
---

## SIMOA 

This MSc thesis investigates personality-related factors associated with the discontinuation of benzodiazepine receptor agonists (BZRAs) used for sleep. Using a machine learning approach, specifically a random forest model, we compare individuals who have stopped using BZRAs with those who continue to use them. Personality is assessed through multiple validated instruments, including the DBAS-16 (Dysfunctional Beliefs and Attitudes about Sleep), BFI-10 (Big Five Inventory), SURPS (Substance Use Risk Profile Scale), and CISS-21 (Coping Inventory for Stressful Situations). The aim is to identify patterns and predictors that distinguish these two groups and provide insight into the psychological and behavioral factors influencing BZRA use.


## Packages and Data Loading

Below I will include all the packages I installed or libraried in for the project. I will aslo load in the data and clean it in this section so that all other sections can use the pre-created data frames rather having to remake it for each section. 

```{r}
#| label: Packages

library(readr)

```

```{r}
#| label: Data Loading

SIMOA <- read_csv("SIMOA Report.csv")
View(SIMOA)

```




You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
